\documentclass[11pt,a4paper]{report}
\usepackage[T1]{fontenc}
\usepackage{isabelle,isabellesym}

% further packages required for unusual symbols (see also
% isabellesym.sty), use only when needed

\usepackage{amssymb}
  %for \<leadsto>, \<box>, \<diamond>, \<sqsupset>, \<mho>, \<Join>,
  %\<lhd>, \<lesssim>, \<greatersim>, \<lessapprox>, \<greaterapprox>,
  %\<triangleq>, \<yen>, \<lozenge>

%\usepackage{eurosym}
  %for \<euro>

\usepackage[only,bigsqcap,bigparallel,fatsemi,interleave,sslash]{stmaryrd}
  %for \<Sqinter>, \<Parallel>, \<Zsemi>, \<Parallel>, \<sslash>

%\usepackage{eufrak}
  %for \<AA> ... \<ZZ>, \<aa> ... \<zz> (also included in amssymb)

\usepackage{textcomp}
  %for \<onequarter>, \<onehalf>, \<threequarters>, \<degree>, \<cent>,
  %\<currency>

\usepackage{wasysym}
\usepackage{pifont}

% this should be the last package used
\usepackage{pdfsetup}

% urls in roman style, theory text in math-similar italics
\urlstyle{rm}
\isabellestyle{it}

% for uniform font size
%\renewcommand{\isastyle}{\isastyleminor}


\begin{document}

\title{Abstract Consistency Properties}
\author{Asta Halkjær Boserup, Anders Schlichtkrull}
\maketitle

\abstract{
  Smullyan and Fitting have used abstract consistency properties to great effect in unifying meta-theoretical results in logic.
  In this work we use locales to mechanize abstract consistency properties without fixing a particular logic or syntax.
  We prove the usual components of abstract consistency properties ---conjunctive, disjunctive, universal, and existential formulas based on Smullyan's uniform notation--- as special cases of our abstract development.
  We follow Fitting's technique for closing a consistency property under limits and finding a maximal element.
  We thus prove the existence of a maximal consistent set, a Hintikka set, for any notion of consistency expressible in the framework.
  Users of the framework can define an abstract consistency property for their own syntax and logic, and prove model existence via our Hintikka sets.

  We provide three example instantiations.
  First, compactness and completeness for a first-order logic where we only instantiate universal quantifiers with already occurring terms.
  Second, completeness over general models of a second-order logic.
  Third, completeness of our own natural deduction system for Prior's Ideal Language, a recently developed hybrid logic with propositional quantification.
}

\tableofcontents

% sane default for proof documents
\parindent 0pt\parskip 0.5ex

% generated text of all theories
\input{session}

\nocite{*}

% optional bibliography
\bibliographystyle{abbrv}
\bibliography{root}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
